---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MotivatoR 📣

<!-- badges: start -->
<!-- badges: end -->

MotivatoR is a simple and light R package designed to provide random motivational messages. It's a fun and encouraging way to keep your spirits high while coding, analyzing data, or navigating through scientific work.

This project was inspired by an idea from Carlos Mora Rubio, to whom I dedicate this package with appreciation.

## Installation

You can install the development version of MotivatoR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak") if you haven't already
install.packages("pak")
pak::pak("luzlongoria/MotivatoR")

```
Or using devtools:

``` r
install.packages("devtools")
devtools::install_github("luzlongoria/MotivatoR")

```

## Example output

This is a basic example which shows you how to solve a common problem:

```{r example}
library(MotivatoR)
## Each time you call motivation(), you will receive a randomly selected motivational quote.
motivation()
"Success doesn’t just find you. You have to go out and get it."
```


